---
title: "C, P, U, NP : HOW TO"
author: "Kenith Grey"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    highlight: pygments
    theme: journal 
---

#Required Libraries#
```{r, message=FALSE, warning=FALSE}
require(ggplot2)
require(ggQC)
```


#Example 1 : c Chart#
##Setup##
```{r Setup Data}
set.seed(5555)
Process1 <- data.frame(Process_run_id=1:30, 
                       Counts=rpois(n = 30, lambda = 25))
c_base <- ggplot(Process1, aes(x=Process_run_id, y = Counts)) 
```

##Basic c chart##
```{r XmR mR Plot, message=FALSE, warning=FALSE, fig.height=6}
c_Chart <- c_base + geom_point() + geom_line() +
       stat_QC(method = "c") +
       stat_QC_labels(method = "c", digits = 2)

c_Chart
```



#Example 2 : c Chart Facet#
##Setup##

```{r Setup C chart facet Data}
set.seed(5555)
Process1 <- data.frame(Process_run_id = 1:30, 
                       Counts=rpois(n = 30, lambda = 25),
                       Group = "A")
Process2 <- data.frame(Process_run_id = 1:30, 
                       Counts = rpois(n = 30, lambda = 5),
                       Group = "B")

all_processes <- rbind(Process1, Process2)

c_base <- ggplot(all_processes, aes(x=Process_run_id, y = Counts)) 
```

##Facted c chart##
```{r faceted c-chart, message=FALSE, warning=FALSE, fig.height=6}
c_Chart <- c_base + geom_point() + geom_line() +
       stat_QC(method = "c") +
       stat_QC_labels(method = "c", digits = 2) +
       facet_grid(.~Group)

c_Chart
```


#Example 3 : np Chart#
##Notes## 

  * The constant "n" must be specified in stat_QC(method = "np", n = ??)
  * chart supports faceting
    
##Setup##
```{r np chart Setup Data}
set.seed(5555)
np_data <- data.frame(
            trial=1:30,
            Number_Nonconforming = rbinom(30, 30, prob = .50),
            n = rep(15, 30))
```

##Basic np chart##
```{r basic np chart, message=FALSE, warning=FALSE, fig.height=6}
np_Chart <- ggplot(data = np_data, aes(trial, Number_Nonconforming)) +
  geom_point() + geom_line() + 
  stat_QC(method = "np", n = 30) +
  stat_QC_labels(method = "np", n = 30)

np_Chart
```




#Example 4 : p Chart#
##Notes## 

  * Here "n" is not constant and must be specified in the ggplot aes().
  * if aes() arg. x is an ordered factor or coersed with as.ordered(), specify group = 1 in ggplot aes(). 
  * chart supports faceting

    
##Setup##
```{r p chart Setup Data}
set.seed(5555)
p_data <- data.frame(trial=1:30,
  Num_Incomplete_Items = rpois(30, lambda = 30),
  Num_Items_in_Set = runif(n = 30, min = 50, max = 100))

p_data$Proportion_Incomplete <- p_data$Num_Incomplete_Items/p_data$Num_Items_in_Set

```

##Basic p chart##
```{r basic p chart, message=FALSE, warning=FALSE, fig.height=6}
p_Chart <- ggplot(data = p_data, aes(trial, y=Proportion_Incomplete,
                            n=Num_Items_in_Set)) +
  geom_point() + geom_line() + 
  stat_QC(method = "p") 

p_Chart
```




#Example 5 : u Chart#
##Notes## 

  * Here "n" is not constant and must be specified in the ggplot aes().
  * if aes() arg. x is an ordered factor or coersed with as.ordered(), specify group = 1 in ggplot aes(). 
  * chart supports faceting
    
##Setup##
```{r u chart Setup Data}
set.seed(5556)
u_data <- data.frame(trial=1:30,
              Num_of_Blemishes = rpois(30, lambda = 30),
              Num_Items_Inspected = runif(n = 30, min = 50, max = 100)
          )

u_data$Blemish_Rate <- u_data$Num_of_Blemishes/u_data$Num_Items_Inspected
```

##Basic u chart##
```{r basic u chart, message=FALSE, warning=FALSE, fig.height=6}
u_chart <- ggplot(data = u_data, aes(x=trial,
                            y=Blemish_Rate,
                            n=Num_Items_Inspected)) +
           geom_point() + geom_line() +
           stat_QC(method = "u")

u_chart
```

