---
title: "stat_mR()"
author: "Kenith Grey"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    highlight: pygments
    theme: journal 
---
***
#Description#

ggplot stat used to create a mR chart in ggplot. As of ggQC v0.0.3, the mR method can be called using stat_QC(method="mR"). 

#Usage#

    stat_mR(mapping = NULL, data = NULL, geom = "point",
      position = "identity", show.legend = NA, inherit.aes = TRUE,
      na.rm = FALSE, color.mr_point = "black", color.mr_line = "black",
      color.qc_limits = "red", color.qc_center = "blue", ...)


#Specialized Args: stat_mR()#
  * **color.mr_point** : color, to be used for the mR points.

  * **color.mr_line**	 : color, to be used for line connecting points.

  * **color.qc_limits**	: color, used to colorize the plot's upper and lower mR control limits.

  * **color.qc_center**	: color, used to colorize the plot's center line.

  * **text.size** : number, size of the text label

  * **...** : other arguments passed on to layer. These are often aesthetics, used to set an aesthetic to a fixed value, like color = "red" or size = 3. They may also be parameters to the paired geom/stat.

***
```{r, include=FALSE}
require(ggplot2)
require(ggQC)
```


#Examples#
```{r Setup Data}
# Setup Data --------------------------------------------------------------
set.seed(5555)
n = 10
Process1 <- data.frame(processID = as.factor(rep(1,n)),
                       metric_value = rnorm(n,0,1),
                       Process_run_id = 1:n)
```

##Base Plot##
 
 This plot below is just the individual values for 10 points sampled out the the normal distribution.
 
```{r Indivduals Chart, fig.width=8, fig.height=4}
#Before ggQC v0.0.3
mr_stat_mR <- ggplot(Process1, aes(x=Process_run_id, y = metric_value)) +
        ggtitle("stat_mR()", subtitle = "Yes, it's blank, go to next section") +
        scale_x_continuous(expand =  expand_scale(mult = .15)) #pad x-axis

#Preparing for stat_QC way of makring plot
mR_Stat_QC <- ggplot(Process1, aes(x=Process_run_id, y = metric_value)) +
  ggtitle("stat_QC(method='mR')", subtitle = "Yes, it's blank, go to next section") +
  scale_x_continuous(expand =  expand_scale(mult = .15)) #pad x-axis

gridExtra::grid.arrange(mr_stat_mR, mR_Stat_QC, nrow=1)
```
   
  To get the mR plot for this data, you just call stat_mR() as shown in the next section. Notice that there is no call for geom_point() or geom_line().
  
##mR Plot##
```{r mR Plot, fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
mR <- mR_Stat_QC +
      stat_mR() +
      ggtitle("stat_mR()", subtitle = "uses stat_mR()")


#example of making graph with stat_QC()
MR2 <- mR_Stat_QC + 
       stat_QC(method = "mR") +
       ggtitle("stat_QC(method='mR')", subtitle = "uses stat_QC()")

gridExtra::grid.arrange(mR, MR2, nrow=1)
```

##mR Plot Lables##
```{r mR Plot Lables, fig.height=4, fig.width=8, message=FALSE, warning=FALSE}

mR <- mR_Stat_QC +
      stat_mR() +
      stat_QC_labels(method = "mR", digits = 3) +
      ggtitle("stat_mR()", subtitle = "uses stat_mR()")
      
MR2 <- mR_Stat_QC + 
       stat_QC(method = "mR", auto.label = T, label.digits = 3) +
       ggtitle("stat_QC(method='mR')", subtitle = "uses stat_QC()")

gridExtra::grid.arrange(mR, MR2, nrow=1)

```

##Change mR Plot Point Color##
```{r Change mR Plot Point Color, fig.height=4, fig.width=8, message=FALSE, warning=FALSE}

mR <- ggplot(Process1, aes(x=Process_run_id, y = metric_value)) +
       stat_mR(color.mr_point = "red") +
       ggtitle("stat_mR()", subtitle = "uses stat_mR()")  

#example of making graph with stat_QC()
MR2 <- mR_Stat_QC + stat_QC(method = "mR", color.point = "red") +
       ggtitle("stat_QC(method='mR')", subtitle = "uses stat_QC()")

gridExtra::grid.arrange(mR, MR2, nrow=1)
```

##Change mR Plot Line Color##
```{r Change mR Plot Line Color, fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
mR <- ggplot(Process1, aes(x=Process_run_id, y = metric_value)) +
       stat_mR(color.mr_line = "purple") +
       ggtitle("stat_mR()", subtitle = "uses stat_mR()")  

#example of making graph with stat_QC()
MR2 <- mR_Stat_QC + stat_QC(method = "mR", color.point = "purple") +
       ggtitle("stat_QC(method='mR')", subtitle = "uses stat_QC()")

gridExtra::grid.arrange(mR, MR2, nrow=1)
```





