---
title: "ggQC HOWTO - stat_pareto()"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    highlight: pygments
    theme: journal 
---

#Description#

ggplot stat function to produce a pareto chart.

#Usage#

    stat_pareto(mapping = NULL, data = NULL, geom = "point", position = "identity", show.legend = NA, inherit.aes = TRUE, group = 1, na.rm = FALSE, point.color = "black", point.size = 2, line.color = "black", line.size = 0.5, bars.fill = c("red", "white"), ...)

#Specialized Args:#

**group** defines grouping for variable for pareto plot, default and suggested is 1.

**point.color** color, used to define point color of cumulative percentage line

**point.size** number, used to define point size of cumulative percentage line

**line.color** color, used to define line color of cumulative percentage line

**line.size** color, used to define line weight of cumulative percentage line

**bars.fill** character vector length 2, start and end colors for pareto bars.

***

#Examples#
```{r,  include=FALSE}
require(ggQC)
require(ggplot2)
```

```{r Setup Data}
# Setup Data --------------------------------------------------------------
 df <- data.frame(
                  x = letters[1:10],
                  y = as.integer(runif(n = 10, min = 0, max=100))
                 )

```

```{r Simple Pareto Plot, fig.width=4, fig.height=4}

# Render Pareto Plot ------------------------------------------------------


ggplot(df, aes(x=x, y=y)) +
 stat_pareto(point.color = "red",
             point.size = 3,
             line.color = "black",
             #size.line = 1,
             bars.fill = c("blue", "orange")
 )
```
