---
title: "stat_QC_labels()"
author: "Kenith Grey"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    highlight: pygments
    theme: journal 
---
***
#Description#

Write QC line lables to ggplot QC Charts. Useful if you want to see the value of the center line and QC limits. see method argument for methods supported.

>This function has been largely replaced by setting stat_QC(auto.label=T) when you specify stat_QC. However, there may be times when stat_QC_labels() provides you with additional control. 

#Usage#

    stat_QC_labels(mapping = NULL, data = NULL, geom = "label",
    position = "identity", na.rm = FALSE, show.legend = NA,
    inherit.aes = TRUE, n = NULL, digits = 1, method = "xBar.rBar",
    color.qc_limits = "red", color.qc_center = "black", text.size = 3,      ...)


#Specialized Args: Stat_QC_labels()#
**n**: number, for

  * Studentized Charts, used for custom or hypothetical subgroup size.
  * np Charts, used to specify a fixed area of opportunity.

**digits** integer, indicating the number of decimal places

**method** : string, calling the following methods:

  * **Individuals Charts**: mR, XmR,
  * **Attribute Charts**: c, np, p, u,
  * **Studentized Charts**: xBar.rBar, xBar.rMedian, xBar.sBar, xMedian.rBar, xMedian.rMedian
  * **Dispersion Charts**: rBar, rMedian, sBar.

**color.qc_limits**	: color, used to colorize the plot's upper and lower mR control limits.

**color.qc_center**	: color, used to colorize the plot's center line.

**text.size** : number, size of the text label

**...**: other arguments passed on to layer. These are often aesthetics, used to set an aesthetic to a fixed value, like color = "red" or size = 3. They may also be parameters to the paired geom/stat.

***

#Examples#
```{r, include=FALSE}
require(ggplot2)
require(ggQC)
```



```{r Setup Data}
# Setup Data --------------------------------------------------------------
set.seed(5555)
Process1 <- data.frame(processID = as.factor(rep(1,100)),
                       metric_value = rnorm(100,0,1),
                       subgroup_sample=rep(1:20, each=5),
                       Process_run_id = 1:100)
```

###Base Plot###
```{r Indivduals Chart, fig.width=4, fig.height=4}
INDV <- ggplot(Process1, aes(x=Process_run_id, y = metric_value)) +
       geom_point() + geom_line() 
INDV
```

###XmR Default Overlay with XmR Labels###
```{r Default XmR with Labels, fig.width=4, fig.height=4}
INDV + stat_QC(method="XmR") +
  stat_QC_labels(method="XmR")
```

###Change Center-Label Color ###
```{r Change Center-Label Color, fig.width=4, fig.height=4}
INDV + stat_QC(method="XmR") +
  stat_QC_labels(method="XmR", color.qc_center = "blue")
```

###Change Limit-Label Color ###
```{r Change Limit-Label Color, fig.width=4, fig.height=4}
INDV + stat_QC(method="XmR") +
  stat_QC_labels(method="XmR", color.qc_limits = "green")
```

###Change Label Size ###
```{r Change Label Size, fig.width=4, fig.height=4}
INDV + stat_QC(method="XmR") +
  stat_QC_labels(method="XmR", text.size = 4)
```