---
title: "HOW TO: XmR & mR Plots"
author: "Kenith Grey"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    highlight: pygments
    theme: journal 
---

#Required Libraries#
```{r, message=FALSE, warning=FALSE}
require(ggplot2)
require(ggQC)
require(gridExtra)
```

#Example 1 : Basic Plot#
##Setup##
```{r Setup Data}
set.seed(5555)
Process1 <- data.frame(processID = as.factor(rep(1,20)),
                       metric_value = rnorm(20,0,1),
                       subgroup_sample=letters[1:20],
                       Process_run_id = 1:20)

INDV <- ggplot(Process1, aes(x=Process_run_id, y = metric_value)) 
```

##Basic XmR-mR Plot##
```{r XmR mR Plot, message=FALSE, warning=FALSE, fig.height=6}
XmR <- INDV + geom_point() + geom_line() +
       stat_QC(method = "XmR") +
       stat_QC_labels(method = "XmR", digits = 2)

mR <- INDV + stat_mR() +
      stat_QC_labels(method = "mR", digits = 2) +
      ylab("mR")

grid.arrange(XmR, mR, ncol=1)
```

#Example 2: x as Factor#
##Setup##
```{r Indivduals Chart-x as factor, fig.width=4, fig.height=4}
INDV <- ggplot(Process1, aes(x=subgroup_sample, y = metric_value)) 
```

##XmR-mR: x as factor (Wrong Way)##

  Oh my! looks like something went horrabily wrong. See fix below using **group** aesthetic.

```{r XmR mR Plot with Factor, message=FALSE, warning=FALSE, fig.height=6}
XmR <- INDV + geom_point() + geom_line() +
       stat_QC(method = "XmR") +
       stat_QC_labels(method = "XmR", digits = 2)

mR <- INDV + stat_mR() +
      stat_QC_labels(method = "mR", digits = 2) +
      ylab("mR")

grid.arrange(XmR, mR, ncol=1)
```

##XmR-mR: x as factor (Right Way)##

Issue solved using **group** asthetic (i.e, group=1). 
```{r Indivduals Chart-x as factor-group, fig.width=4, fig.height=4}
INDV <- ggplot(Process1, aes(x=subgroup_sample, y = metric_value, group=1)) 
```

```{r XmR mR Plot with Factor-group, message=FALSE, warning=FALSE, fig.height=6}
XmR <- INDV + geom_point() + geom_line() +
       stat_QC(method = "XmR") +
       stat_QC_labels(method = "XmR", digits = 2)

mR <- INDV + stat_mR() +
      stat_QC_labels(method = "mR", digits = 2) +
      ylab("mR")

grid.arrange(XmR, mR, ncol=1)
```

#Example 3: XmR mR Faceting#
##Setup Faceting Data##

Here we are using two processes and binding the data together into one data.frame
```{r Faceting Setup Data}
set.seed(5555)
Process1 <- data.frame(processID = as.factor(rep(1,20)),
                       metric_value = rnorm(20,0,1),
                       subgroup_sample=letters[1:20],
                       Process_run_id = 1:20)
Process2 <- data.frame(processID = as.factor(rep(2,20)),
                       metric_value = rnorm(20,5,2),
                       subgroup_sample=letters[1:20],
                       Process_run_id = 1:20)

BothProcesses <- rbind(Process1, Process2)
```

##ggplot Faceting Init##
```{r Facet Indivduals Chart, fig.width=4, fig.height=4}
INDV <- ggplot(BothProcesses, aes(x=Process_run_id, y = metric_value)) 
```

##Basic XmR-mR Facet Plot##
```{r Facet XmR mR Plot, message=FALSE, warning=FALSE, fig.height=6}
XmR <- INDV + geom_point() + geom_line() +
       stat_QC(method = "XmR") +
       stat_QC_labels(method = "XmR", digits = 2) +
       facet_grid(.~processID)

mR <- INDV + stat_mR() +
      stat_QC_labels(method = "mR", digits = 2) +
      ylab("mR") +
      facet_grid(.~processID)

grid.arrange(XmR, mR, ncol=1)
```
